curatedMetagenomicData

### 2020-01-27 manuscript_NS_MRD.Rmd
updated

pseq.subset <- subset_samples(pseq.subset, !is.na(nationality) )
atlas.pseq <- subset_samples(atlas.pseq, !is.na(nationality) )

@@

plot_abundance.ak = function(pseq.subset,title = "",
                         Facet = "Genus", Color = "Phylum"){
 # Arbitrary subset, based on Phylum, for plotting
 p1f = subset_taxa(pseq.subset, Genus %in% c("Akkermansia"))
 mphyseq = psmelt(p1f)
 mphyseq <- subset(mphyseq, Abundance > 0)
 p <- ggplot(data = mphyseq, mapping = aes_string(x = "mnd",y = "Abundance")) +
   geom_violin(fill = NA) +
   geom_point(size = 1, alpha = 0.3,
              position = position_jitter(width = 0.3)) + scale_y_log10()+
   theme(legend.position="none") + scale_colour_manual(values = wes_palette(glob_theme)) 
 #library(rms)
#fita <- lrm(mnd ~ gender + log(Abundance) + bmi_group + age_category, data =mphyseq)
#fita <- lrm(mnd ~ gender + log(Abundance) , data =mphyseq)
#fita <- lrm(mnd ~ gender + log(Abundance) + bmi_group, data =mphyseq)

save_plot(paste("akkermansia_",title_text,".png", sep = "" ), p)
}

plotAtlas = plot_abundance.ak(atlas.pseq, "atlas")
plotCur = plot_abundance.ak(pseq.subset, "curated")
grid.arrange(nrow = 2, plotAtlas, plotCur)

>>>>

pseq.subset <- subset_samples(pseq.subset, !is.na(nationality) )
atlas.pseq <- subset_samples(atlas.pseq, !is.na(nationality), !is.na(mnd))

@@

plot_abundance.ak = function(pseq.subset,title = "",
                         Facet = "Genus", Color = "Phylum"){
 # Arbitrary subset, based on Phylum, for plotting
 p1f = subset_taxa(pseq.subset, Genus %in% c("Akkermansia"))
 mphyseq = psmelt(p1f)
 mphyseq <- subset(mphyseq, Abundance > 0)
 p <- ggplot(data = mphyseq, mapping = aes_string(x = "mnd",y = "Abundance")) +
   geom_violin(fill = NA) +
   geom_point(size = 1, alpha = 0.3,
              position = position_jitter(width = 0.3)) + scale_y_log10()+
   theme(legend.position="none") + scale_colour_manual(values = wes_palette(glob_theme)) + theme_classic() + xlab('MND DALYs')
 #library(rms)
#fita <- lrm(mnd ~ gender + log(Abundance) + bmi_group + age_category, data =mphyseq)
#fita <- lrm(mnd ~ gender + log(Abundance) , data =mphyseq)
#fita <- lrm(mnd ~ gender + log(Abundance) + bmi_group, data =mphyseq)

#save_plot(paste("akkermansia_",title_text,".png", sep = "" ), p)
}

plot_abundance.ak(atlas.pseq, "atlas")
plot_abundance.ak(pseq.subset, "curated")

#plotAtlas <- plot_abundance.ak(atlas.pseq, "atlas")
#plotCur <- plot_abundance.ak(pseq.subset, "curated")
#plot(grid.arrange(nrow = 2, plotAtlas, plotCur))
